FinalManuscript_DISCS_UG

### 2019-01-21 pcsc-paper/parts/03_exponentialandlogarithmic.tex
Briefly referenced new graphs
Briefly referenced new graphs

\section{Exponential and Logarithmic Functions}
We now present our main contribution in this paper: a general method to improve the general accuracy of the logarithm approximation given by Khattri in~\cite{khattri_new_2009} for use in privacy-preserving calculation, provided that accuracy is only required for a specific range.

>>>>

\section{Logarithmic Function Approximation}
We now present our main contribution in this paper: a general method to improve the general accuracy of the logarithm approximation given by Khattri in~\cite{khattri_new_2009} for use in privacy-preserving calculation, provided that accuracy is only required for a specific range.

### 2019-01-21 pcsc-paper/parts/04_inversetrig.tex
Briefly referenced new graphs
Briefly referenced new graphs

\section{Inverse Trigonometric Functions}
We will now show how a Gauss--Legendre quadrature approach can also be used for efficient privacy-preserving approximation of the inverse tangent function. Two well-known series representations of the inverse tangent function exist: the Maclaurin series expansion,
\begin{align} \label{eq:arctan_maclaurin}
	\arctan x = \sum_{n=0}^{\infty}{\frac{(-1)^nx^{2n+1}}{2n+1}}, \text{ for }|x|\leq 1,
\end{align}
and the following series expansion discovered by Euler in 1755, which converges more rapidly for all $x$~\cite{chien-lih_89.67_2005}.
\begin{align} \label{eq:arctan_euler}
	\arctan x = \sum_{n=0}^{\infty}
	{
	\frac
		{2^{2n}(n!)^2}
		{(2n+1)!}
	\frac
		{x^{2n+1}}
		{(1+x^2)^{n+1}}
	}.
\end{align}
We will compare the quadrature approach with the method of computing partial sums from each of these series.

>>>>

\section{Inverse Tangent Function Approximation}
We will now show how a Gauss--Legendre quadrature approach can also be used for efficient privacy-preserving approximation of the inverse tangent function. Two well-known series representations of the inverse tangent function exist: the Maclaurin series expansion,
\begin{align} \label{eq:arctan_maclaurin}
	\arctan x = \sum_{n=0}^{\infty}{\frac{(-1)^nx^{2n+1}}{2n+1}}, \text{ for }|x|\leq 1,
\end{align}
and the following series expansion discovered by Euler in 1755, which converges more rapidly for all $x$~\cite{chien-lih_89.67_2005}.
\begin{align} \label{eq:arctan_euler}
	\arctan x = \sum_{n=0}^{\infty}
	{
	\frac
		{2^{2n}(n!)^2}
		{(2n+1)!}
	\frac
		{x^{2n+1}}
		{(1+x^2)^{n+1}}
	}.
\end{align}
We will compare the quadrature approach with the method of computing partial sums from each of these series.

### 2019-01-21 pcsc-paper/parts/05_testsforaccuracy.tex
Briefly referenced new graphs
Briefly referenced new graphs

We note that the privacy-preserving floating-point arithmetic resulted in some degree of floating-point error, as the observed floating point error in Table~\ref{tab:log_approximation} is greater than the raw absolute error observed in Figure~\ref{fig:log_error_comparison}. However, it can still be seen that the error of the scaled approximation is less than that of the original approximation for large inputs, although this approximation loses accuracy for smaller inputs.
\begin{table}[ht]
	\caption{Comparison of logarithm approximation errors under Paillier}
	\label{tab:log_approximation}
	\begin{tabular}{lcc}
		\toprule
		Input & Original quadrature & Scaled quadrature\\
		\midrule
		$\log 1$ & $0$ & $2.053729 \times 10^{-2}$\\
		$\log 10$ & $2.833179 \times 10^{-2} $ & $2.280124 \times 10^{-1}$\\
		$\log 50$ & $2.170779 \times 10^{-2}$ & $2.437148 \times 10^{-2}$\\
		$\log 100$ & $3.524916 \times 10^{-1}$ & $2.122159 \times 10^{-2}$\\
		$\log 200$ & $8.859869 \times 10^{-1}$ & $1.441611 \times 10^{-1}$\\
		$\log 256$ & $1.098463 \times 10^{0}$ & $1.993136 \times 10^{-1}$\\
	\bottomrule
\end{tabular}
\end{table}

@@

\subsection{Inverse Tangent Approximation}
We also computed $\arctan x$ using for various encrypted inputs using both the first five terms of Euler's series for the inverse tangent function (Equation~\ref{eq:arctan_euler_partial}) and our quadrature approximation (Equation~\ref{eq:arctan_quadrature}). These were compared with the values returned by the built-in inverse tangent function in Python. We show several data points in Table~\ref{tab:arctan_approximation}. Similar to the logarithm approximations, we note that there is a degree of floating-point error compared to that predicted by Figure~\ref{fig:arctan_error}, but the quadrature approach obtains higher accuracy despite requiring a similar number of floating-point operations to execute.

>>>>

We note that the privacy-preserving floating-point arithmetic resulted in some degree of floating-point error, as the observed floating point error in Table~\ref{tab:log_approximation} is greater than the raw absolute error observed in Figure~\ref{fig:log_error_comparison}. Figure~\ref{fig:comp_log} shows a plot of the observed absolute error of the original quadrature approximation and scaled quadrature approximation to the logarithm, when computed using privacy-preserving arithmetic through the Paillier cryptosystem. While there are intervals where the original quadrature approximation is more accurate than the scaled quadrature approximation, we can see that the scaled quadrature is more accurate for larger inputs.

\begin{table}[ht]
	\caption{Comparison of logarithm approximation errors under Paillier}
	\label{tab:log_approximation}
	\begin{tabular}{lcc}
		\toprule
		Input & Original quadrature & Scaled quadrature\\
		\midrule
		$\log 1$ & $0$ & $2.053729 \times 10^{-2}$\\
		$\log 10$ & $2.833179 \times 10^{-2} $ & $2.280124 \times 10^{-1}$\\
		$\log 50$ & $2.170779 \times 10^{-2}$ & $2.437148 \times 10^{-2}$\\
		$\log 100$ & $3.524916 \times 10^{-1}$ & $2.122159 \times 10^{-2}$\\
		$\log 200$ & $8.859869 \times 10^{-1}$ & $1.441611 \times 10^{-1}$\\
		$\log 256$ & $1.098463 \times 10^{0}$ & $1.993136 \times 10^{-1}$\\
	\bottomrule
\end{tabular}
\end{table}

@@

\subsection{Inverse Tangent Approximation}
We also computed $\arctan x$ using for various encrypted inputs using both the first five terms of Euler's series for the inverse tangent function (Equation~\ref{eq:arctan_euler_partial}) and our quadrature approximation (Equation~\ref{eq:arctan_quadrature}). These were compared with the values returned by the built-in inverse tangent function in Python. We show several data points in Table~\ref{tab:arctan_approximation}, and show graphs of the observed error in Figure~\ref{fig:comp_arctan}. Similar to the logarithm approximations, we note that there is a degree of floating-point error compared to that predicted by Figure~\ref{fig:arctan_error}, but the quadrature approach obtains higher accuracy despite requiring a similar number of floating-point operations to execute.
